Multi-line Intensity Mapping

### 2019-04-27 paper/ms.tex
Silence crap about CO line

\subsection{\CO{} Forecasts for CCAT-p and CONCERTO} \label{ssec:forecasts_tf}
Armed with some intuition from the simple white noise-dominated case, we now
turn to forecasting constraints that can be placed on the CO bias factors. Our
modelling of the \CO{} intensity as a function of redshift follows
\citet{2016ApJ...825..143L} and is outlined in Appendix~\ref{app:co_int}. We
assume that $b_i=3$ for each \CO{} line.

>>>>

\subsection{Three-field \CO{} Forecasts for CCAT-p} \label{ssec:forecasts_tf}
% \begin{figure}[h!]
% \begin{center}
% \includegraphics{fig/CO_tf.pdf}
% \end{center}
% \caption{Constraints that can be placed on the fluctuations of the \CO(6-5),
% \CO(5-4), and \CO(4-3) lines with CCAT-p at $z_{\text{obs}} = 0.88$. This
% Figure is purely illustrative, as we do not include noise contributions from
% residual foreground contamination or interloper/extraloper lines. According to
% our simple \CO{} model, we have that $B_{\text{6-5}}, B_{\text{5-4}},
% B_{\text{4-3}} = 151, 183, 232\,\text{Jy}/\text{str}$. Using the instrumental
% specifications in \citet{2018arXiv181208135C}, we find that $N_{\text{6-5}},
% N_{\text{5-4}}, N_{\text{4-3}} = 5.1\times10^9, 1.4\times10^9,
% 5.4\times10^8\,\left(\text{Jy}/\text{str}\right)^2\,\Mpc^3$. We find the same
% behavior as in Figure~\ref{fig:tf_Nconst}, where the best-measured line is
% strongly negatively degenerate with the second-best measured line, the
% best-measured and worst-measured are slightly negatively degenerate, and the
% second-best measured line and the worst-measured are slightly positively
% degenerate. }
% \label{fig:CO_tf}
% \end{figure}

% Armed with some intuition from the simple white noise-dominated case, we now
% turn to forecasting constraints that can be placed on the \CO{} bias factors.
% Our modelling of the \CO{} intensity as a function of redshift follows
% \citet{2016ApJ...825..143L} and is outlined in Appendix~\ref{app:co_int}. We
% assume that $b_i=3$ for each \CO{} line.

% At $z=0.88$, the lines \CO(6-5) ($\nu_{\text{obs}} = 367\,\MHz$), \CO(5-4)
% ($\nu_{\text{obs}} = 306\,\MHz$), and \CO(4-3) ($\nu_{\text{obs}} =
% 245\,\MHz$) are all in the observing band of CCAT-p. We only include
% instrumental noise for this Subsection, neglecting foreground and
% interloper/extraloper contamination. We simply want to place the result of
% Section~\ref{ssec:tf_noisedom} in the context of an actual experiment.

% Using our \CO{} modelling, we find that $B_{\text{6-5}}, B_{\text{5-4}},
% B_{\text{4-3}} = 151, 183, 232\,\text{Jy}/\text{str}$ at $z=0.88$. Using the
% instrumental specifications in \citet{2018arXiv181208135C}, we find that
% $N_{\text{6-5}}, N_{\text{5-4}}, N_{\text{4-3}} = 5.1\times10^9,
% 1.4\times10^9, 5.4\times10^8\,\left(\text{Jy}/\text{str}\right)^2\,\Mpc^3$. We
% assume the instrumental noise is white, but note that in this case the
% noise-dominated assumption is mildly broken. The worst case is that of the
% \CO(4-3) line, where on a scale of $k\sim0.01\,\Mpc^{-1}$ we have that
% $P_{\text{4-3}} \sim 3N_{\text{4-3}}$. Again, this Subsection is purely
% illustrative, and we will rectify these assumptions in the next Section.

% We assume a bandwidth of $60\,\MHz$ for the line \CO(6-5). This corresponds to
% a redshift band of width $\Delta z = 0.16$. We resize the \CO(5-4) and
% \CO(4-3) bands to have the same extent in redshift space, which means slightly
% scaling the frequency bandwidth --- in this case, the bandwidths are $50$ and
% $40\,\MHz$, respectively. In Figure~\ref{fig:CO_tf} we show the constraints
% that can be placed on each of $B_{\text{6-5}}$, $B_{\text{5-4}}$, and
% $B_{\text{4-3}}$. The line \CO(4-3) is measured to the best intrinsic \SN{},
% followed by \CO(5-4) and then \CO(6-5). We find the same behavior as in
% Section~\ref{ssec:tf_noisedom}, where the best-measured line is strongly
% negatively degenerate with the second-best measured line, the best-measured
% and worst-measured are slightly negatively degenerate, and the second-best
% measured line and the worst-measured are slightly positively degenerate.
% However, we find that CCAT-p should be able to make a measurement of each bias
% factor using the three-field approach.
